Strong lensing selection effects

### 2023-06-26 paper/reply_to_referee.txt

We thank the referee for the useful suggestions. We have addressed the points raised in the report, as explained below.

- "The authors have a novel definition of a lens, and a toy definition of lens finding. The results are likely very sensitive to these definitions (indeed their conclusion about source size biases is demonstrably at odds with other authors because they have different definitions of a detectable lens). The authors should investigate which of their results are robust to different definitions of a lens and a discovered lens, and which findings are not robust e.g. if they impose a minimum magnification cut, or only choose objects with a centroid within the caustic."

Reply - We added a subsection in the Discussion (6.7) to check how the key results vary with a magnification-based lens definition.

@@

Reply - We're a bit unsure about how to address this point. We believe that the quantitative statements in the conclusions (particularly bullet point 6 and 8) already give an answer to this question.

- "I found the introduction to get very technical, very quickly. Equation 1 isn't really an equation, more an illustration of what goes into the discovered lens population. I think a bit more qualitative text about lensing selection biases would be helpful before jumping in to equation 1."

Reply - We restructured the introduction accordingly.

Finally, we added a section to the Discussion to address the issue of lens vs. source selection (section 6.6).

### 2023-06-26 paper/seleff.tex
adding lens-source selection
reply to referee

>>>>

\subsection{Lens vs. source selection}

{\bf
The simulations described in \Sref{sect:sims}, on which our experiment is based, are examples of so-called lens-selected surveys:
the lens samples are built by first defining a population of possible lens galaxies and then searching for strong lenses among them. Photometric lens searches are typically carried out in this way \citep[see e.g.][]{Gav++12,Son++18,Pet++19}.
An alternative approach is to build a source-selected sample, by first searching for signatures of strong lensing within a population of possible background sources and then obtaining information on the lens galaxies \citep[see e.g.][]{Hez++13}.
In principle, these two approaches lead to different strong lensing biases. %Therefore, strictly speaking, our results only apply to a lens-selected sample.
%For example, from \Fref{fig:lenspars} we can see that the distribution in redshift and stellar mass of the lenses extends beyond the bounds applied to the population of foreground galaxies: in principle, a source-based selection method 
For example, from \Fref{fig:lenspars} we can see that the stellar mass distribution of the lenses extends below the minimum mass cut that we applied to the population of foregrounds galaxies: a source-based search that is able detect those lenses would result in a different sample and a different associated strong lensing bias.
However, when considering only lenses with $\tein > 1''$, lens-selection and source-selection yield the same sample (see red histogram in \Fref{fig:lenspars}): in the limit of large Einstein radius, the two operations (identifying suitable lens galaxies and detecting a strongly lensed source) commute.

%In general, speaking of a lens- or source-selected sample is improper.
In general, there is no such thing as a purely lens- or source-selected sample. 
A lens-based search is always also source-based, because a detection of the lensed source is required to identify a lens.
A source-based search is also lens-based, because the lens properties determine important observational features of the lensed source, such as the number of images, the image separation and the total flux.
}
